---
title       : Plot Linear Regressions between two Market Securities
subtitle    : Project for the Developing Data Products Class
author      : Walter Oliver
job         : Data Scientist
framework   : io2012        # {io2012, html5slides, shower, dzslides, ...}
highlighter : highlight.js  # {highlight.js, prettify, highlight}
hitheme     : tomorrow      # 
widgets     : []            # {mathjax, quiz, bootstrap}
mode        : selfcontained # {standalone, draft}
knit        : slidify::knit2slides
---

## Using regression in Finance

1. Regression is a widely used statistical tool in economics, finance and trading
2. Linear Regression between two stocks is useful to help make investing decisions
3. This presentation describes a Web application that provides a regression Plot between two stocks

--- .class #id 

## Visualizing regression between two Stocks

1. The application performs Linear Regression between two stocks and Plots the resulting Regression Line
2. You can access the application here: https://walterov.shinyapps.io/ShinyProject/
3. The application is interactive: it lets users enter any two stock symbols and generate the plot
4. It does not provide the statistics of the model: coeficients, p-value, t-statistic, or residuals. This are future enhancements for the subsequent version

--- .class #id 

## Example of what the application allows you to do

1. Assume you enter these two stock symbols: AAPL and QQQ
2. The output will be the following plot:
<div>
```{r Plot, echo=FALSE, message=FALSE, warning=FALSE}
library(quantmod)
#load the security symbols
#symbols examples: "AAPL", "QQQ"
symbols <- c("AAPL", "QQQ")
stock1 <- getSymbols(symbols[1], src='yahoo', auto.assign = FALSE)
stock2 <- getSymbols(symbols[2], src='yahoo', auto.assign = FALSE)

#define training set
startT  <- "2007-01-01"
endT    <- "2016-07-22"
rangeT  <- paste(startT,"::",endT,sep ="")
tstock1   <- stock1[,6][rangeT]
tstock2   <- stock2[,6][rangeT]

#compute price differences
pdtstock1 <- diff(tstock1)[-1]
pdtstock2 <- diff(tstock2)[-1]

#build the model
model  <- lm(pdtstock1 ~ pdtstock2 - 1)

#plot the regression line
plot(as.vector(pdtstock2),as.vector(pdtstock1), col = "blue", 
     xlab = symbols[2], ylab = symbols[1],
     main = paste(symbols[1], "vs.", symbols[2], sep = " "))
abline(model)

```
</div>

--- .class #id

## Next version

The next version will provide the details of the model as well. For example:

```{r Summary, echo=FALSE, message=FALSE, warning=FALSE}
summary(model)
```
